Code Appendix

### 2017-03-26 Rmd/code.Rmd
Update and re-compile code book for supplementals

# mask out all joint NAs
gti <- lapply(gti, function(x) mask(x, namask))
lclist <- lapply(lclist, function(x) mask(x, namask))

@@

save(dlist_act, file = full_path(p_data, "d_grid_act.rda"))
save(dlist_abs, file = full_path(p_data, "d_grid_abs.rda"))

@@

### Total error
Calculate how much cropland estimates differ between datasets
```{r, eval = FALSE}
paths <- full_path(p_data, dir(p_data, paste0("cover*.*sum_mask.tif$")))
gti <- lapply(paths, raster)
names(gti) <- c("g2007", "g2011")
gti <- lapply(gti, function(x) mask(x, namask))  # apply namask
snms <- c("sa30", "globmu", "modmu", "geow")  # all lc data (no MOD/GC extremes)

# recreate cropland percentages
lc2007 <- lapply(snms, function(x) gti$g2007 - dlist_act[[x]]$f1$g2007)
lc2011 <- lapply(snms, function(x) gti$g2011 - dlist_act[[x]]$f1$g2011)
# plot(lc2007[[2]] - lc2011[[2]])  # same thing, as it should be

# calculate km2 cropland in LC datasets
lckm2 <- sapply(lc2011, function(x) cellStats(x / 100, sum))
refkm2 <- sapply(gti, function(x) cellStats(x / 100, sum))
refkm2[2] / refkm2[1]  # 3.6 percent more in 2011 than 2007

# bias in total cropland relative to GTI
stats2007 <- round((refkm2[2] - lckm2) / refkm2[2] * 100, 1)
stats2011 <- round((refkm2[1] - lckm2) / refkm2[1] * 100, 1)

# N km^2 in country
#sapply(lc2007, function(x) cellStats(!is.na(x), sum))
# sapply(lc2011, function(x) cellStats(!is.na(x) , sum))
# sapply(gti, function(x) cellStats(!is.na(x) , sum))
totkm2 <- cellStats(!is.na(gti$g2011) , sum)
save(stats2007, stats2011, totkm2, refkm2, 
     file = full_path(p_data, "total-cropland.rda"))
```

@@

@@

lc_ag2 <- lapply(snms, function(x) {
  sapply(names(lc_agg), function(y) lc_agg[[y]][[x]])
})  # reshape lc_ag2 -> landcover fractions in outer list
gti_ctot2 <- sapply(1:length(gti_c), function(x) {
  msk <- gti_agg[[x]]$gti > 0.005  # farmland > 0.05% mask
  # msk <- gti_agg[[x]]$gti > 0.05  # farmland > 0.05% mask
  msked <- mask(gti_c[[x]] * tareas[[x]], msk, maskvalue = 0)
  cellStats(msked, sum)
})  # gti 
lc_ctot2 <- lapply(1:length(lc_c2), function(x) {
  xx <- lc_c2[[x]]  # recycle reshaped lc_c2 list
  jj <- lc_ag2[[x]]  # recycle reshaped lc_c2 list
  sapply(1:length(xx), function(y) {
    msk <- jj[[y]] > 0.005  # farmland > 0.05% mask
    # msk <- jj[[y]] > 0  # farmland > 0.05% mask
    msked <- mask(xx[[y]] * tareas[[y]], msk, maskvalue = 0)
    cellStats(msked, sum)
  })
})  # landcover carbon estimates

@@

# Combine tables for output to supplementals, 1 km % differences for country
# and agricultural levels
totc_out <- rbind(t(sapply(totc_cntry, function(x) x[, 1])),
                  t(sapply(totc_crop, function(x) x[, 1])))
pnms <- c("Forest", "Secondary", "Shrubland", "Grassland", "Sparse")
knms <- rep(mcap, 2)
totc_out <- cbind.data.frame(knms, round(unname(totc_out), 2))
colnames(totc_out) <- c("Map", pnms)
totc_out <- cbind(Region = c(rep("Country", 4), rep("Agricultural", 4)), 
                  totc_out)
caption <- paste("Percent differences in total carbon stock estimates", 
                 "calculated from the reference maps and from each of the four",
                 "cropland maps. Differences are evaluated for total carbon",
                 "estimates either at the country scale or over just the",
                 "agricultural regions (cropland $>$0.05\\%), using",
                 "the carbon densities of 5 different cover types to provide", 
                 "the values for the non-agricultural portions of each pixel",  
                 "(cover types indicated by column names).")
totc_xtab <- xtable(totc_out, caption = caption, digits = 1)
print(totc_xtab, type = "latex", caption.placement = "top",
      file = "paper/figures/totC-bias.tex", include.rownames = FALSE)

@@

# check error stats - do they match alternate approaches?
for(i in c("f1", "f25", "f10")) { # i <- "f1"
  for(j in c("sa30", "modmu", "geow")) { # j <- "modmu"
    for(k in c("forest", "shrub", "sparse", "second")) {  # k <- "second"
      print(paste("cross-checking calculations in", i, j, k))
      ref <- gti_agg[[i]][[1]]
      awgts <- area_wgts[[i]][[1]]
      rerror <- c_pct_diff[[i]][[j]]
      a1 <- bias_statsw(ref, awgts, rerror, LC, wm, "mu", 
                        aweight = FALSE)[, get(k)]
      a2 <- bias_statsw(ref, awgts, rerror, LC, wm, "mu", 
                        rweight = FALSE, aweight = FALSE)[, get(k)]
      a3 <- bias_statsw(ref, awgts, rerror, LC, wm, "mu")[, get(k)]
      c1 <- getValues(c_pct_diff[[i]][[j]][[k]])
      w1 <- getValues(gti_agg[[i]][[1]])
      w2 <- getValues(area_wgts[[i]][[1]])
      print("...non-area weighted mean matches?")
      print(a1 == round(weighted.mean(c1, w1, na.rm = TRUE), 2))
      print("...totally unweighted mean matches?")
      print(a2 == round(cellStats(rerror[[k]], mean), 2))
      print("...double weighted mean matches?")
      print(a3 == round(weighted.mean(c1, w1 * w2, na.rm = TRUE), 2))
    }
  }
}

````

@@

caption <- paste("Biases and mean absolute errors (as \\%) for",              
                 "evapotranspiration variables derived from a 29-year time",
                 "series calculated by the VIC model, including the average", 
                 "total ET for the", 
                 "3 months of the year when ET is highest, the annual mean", 
                 "and the minimum and maximum annual ETs in the time series.")
mutab_xtab <- xtable::xtable(mutab, digits = 1, caption = caption)
print(mutab_xtab, type = "latex", file = "paper/figures/et-bias.tex",
      tabular.environment = "longtable", floating = FALSE, 
      caption.placement = "top", include.rownames = FALSE)
```

@@

# data.table calculations
gti_dt <- na.omit(as.data.table.raster(gtis, xy = TRUE))
setkey(gti_dt, prov)
cf <- gti_dt[, list("carea" = sum(f), "parea" = length(f), 
                    "cf" = sum(f) / length(f)), by = prov]
# cftest - cf[, 2:4, with = FALSE]  # close, but diff caused by few NAs in provr

# data.table approach is much more efficient

@@

save(list = ls(), file = full_path(p_data, "yield-bias.rda"))
```

@@

@@

```{r, eval=FALSE}
library(rgdal)
library(SAcropland)
library(rgeos)

@@

Area of sub-Saharan Africa and South Africa's share of that area
```{r, eval=FALSE}
eco <- readOGR(dsn = full_path(p_dat, "africa_ecofloristic_zones.sqlite"), 
               layer = "africa_ecofloristic_zones")
eco@proj4string <- CRS(projection(raster(nrow = 1, ncol = 1)))
af <- readOGR(dsn = full_path(p_dat, "africa_countries_alb.sqlite"), 
               layer = "africa_countries_alb")
af@data <- af@data[, c(1, 3:4)]
ecoalb <- spTransform(eco, af@proj4string)

@@

nosahara <- ecoalb[-sahara, ]
plot(nosahara, col = "red")

ovs <- which(!is.na(over(nosahara, ssa)))
ssaeco <- nosahara[ovs, ]
ssaeco <- ssaeco[-1, ]  # drop a couple Saharan mountains
ssaeco <- ssaeco[-1, ]
# plot(ssaeco[ssaeco@data$gez_term == "Tropical mountain system", ][1, ])
plot(ssa)
plot(ssaeco, col = "red", add = TRUE)

@@

```{r, eval=FALSE}
a <- sample(1:100, size = 20)
b <- sample(1:80, size = 20)
mean(a - b)
sum(a) / sum(b)

>>>>

# mask out all joint NAs
gti <- lapply(gti, function(x) raster::mask(x, namask))
lclist <- lapply(lclist, function(x) raster::mask(x, namask))
cropl <- c(gti$g2011, lclist[c("sa30", "globmu", "modmu", "geow")])
names(cropl)[1] <- "gti"
save(cropl, file = "external/ext_data/cropland-1km.rda")
```

@@

save(lc_agg, gti_agg, area_wgts, file = full_path(p_data, "agg_cropland.rda"))
save(dlist_act, file = full_path(p_data, "d_grid_act.rda"))
save(dlist_abs, file = full_path(p_data, "d_grid_abs.rda"))

@@

### Total error
Calculate how much cropland estimates differ between datasets
```{r, eval = FALSE}
fact <- c(5, 10, 25, 50, 100)
paths <- full_path(p_data, dir(p_data, paste0("cover*.*sum_mask.tif$")))
gti <- lapply(paths, raster)
names(gti) <- c("g2007", "g2011")
gti <- lapply(gti, function(x) raster::mask(x, namask))  # apply namask
snms <- c("sa30", "globmu", "modmu", "geow")  # all lc data (no MOD/GC extremes)

# recreate cropland percentages
# lc2007 <- lapply(snms, function(x) gti$g2007 - dlist_act[[x]]$f1$g2007)
# lc2011 <- lapply(snms, function(x) gti$g2011 - dlist_act[[x]]$f1$g2011)
# plot(lc2007[[2]] - lc2011[[2]])  # same thing, as it should be

# calculate km2 cropland in LC datasets
awgts <- lapply(area_wgts, function(x) x[[1]])
lckm2 <- do.call(rbind, lapply(1:length(lev), function(x) {  # x <- 1
  gtia <- cellStats(gti_agg11[[x]] / 100 * awgts[[x]], sum)
  lca <- sapply(snms, function(y) {
    cellStats(lc_agg[[x]][[y]] / 100 * awgts[[x]], sum)
  })
  o <- c(gtia, lca)
}))
colnames(lckm2)[1] <- "gti"
rownames(lckm2) <- lev

bias_statsw

# mean (stays about the same)
lckmmu <- do.call(rbind, lapply(1:length(lev), function(x) {  # x <- 1
  gtia <- cellStats(gti_agg11[[x]] / 100, mean)
  lca <- sapply(snms, function(y) {
    cellStats(lc_agg[[x]][[y]] / 100, mean)
  })
  o <- c(gtia, lca)
}))
colnames(lckmmu)[1] <- "gti"
rownames(lckmmu) <- lev

# variance declines with scale, as expected
lckmvar <- do.call(rbind, lapply(1:length(lev), function(x) {  # x <- 1
  gtia <- cellStats(gti_agg11[[x]] / 100, var)
  lca <- sapply(snms, function(y) {
    cellStats(lc_agg[[x]][[y]] / 100, var)
  })
  o <- c(gtia, lca)
}))
colnames(lckmvar)[1] <- "gti"
rownames(lckmvar) <- lev

# lckm2 <- sapply(lc_agg$f1[snms], function(x) cellStats(x / 100, sum))
# lckm2 <- sapply(lc2011, function(x) cellStats(x / 100, sum))
# refkm2 <- sapply(gti, function(x) cellStats(x / 100, sum))

# area of each GTI dataset
refkm2 <- sapply(gti_agg$f1, function(x) cellStats(x / 100, sum))
refkm2[2] / refkm2[1]  # 3.7 percent more in 2011 than 2007

# bias in total cropland relative to GTI, at 1 km scale
stats2007 <- round((refkm2[2] - lckm2[1, ]) / refkm2[2] * 100, 1)
stats2011 <- round((refkm2[1] - lckm2[2, ]) / refkm2[1] * 100, 1)

# N km^2 in country
#sapply(lc2007, function(x) cellStats(!is.na(x), sum))
# sapply(lc2011, function(x) cellStats(!is.na(x) , sum))
# sapply(gti, function(x) cellStats(!is.na(x) , sum))

totkm2 <- cellStats(!is.na(gti_agg$f1$g2011), sum)
save(stats2007, stats2011, totkm2, refkm2, 
     file = full_path(p_data, "total-cropland.rda"))
```

@@

# save for further analysis
save(gti_c, lc_c, file = full_path(p_data, "carbon-tier1.rda"))
```

@@

lc_ag2 <- lapply(snms, function(x) {
  sapply(names(lc_agg), function(y) lc_agg[[y]][[x]])
})  # reshape lc_ag2 -> landcover fractions in outer list
gti_ctot2 <- sapply(1:length(gti_c), function(x) {
  msk <- gti_agg[[x]]$gti > 0.005  # farmland > 0.05% mask
  # msk <- gti_agg[[x]]$gti > 0.05  # farmland > 0.05% mask
  msked <- raster::mask(gti_c[[x]] * tareas[[x]], msk, maskvalue = 0)
  cellStats(msked, sum)
})  # gti 
lc_ctot2 <- lapply(1:length(lc_c2), function(x) {
  xx <- lc_c2[[x]]  # recycle reshaped lc_c2 list
  jj <- lc_ag2[[x]]  # recycle reshaped lc_c2 list
  sapply(1:length(xx), function(y) {
    msk <- jj[[y]] > 0.005  # farmland > 0.05% mask
    # msk <- jj[[y]] > 0  # farmland > 0.05% mask
    msked <- raster::mask(xx[[y]] * tareas[[y]], msk, maskvalue = 0)
    cellStats(msked, sum)
  })
})  # landcover carbon estimates

@@

# Combine tables for output to supplementals, 1 km % differences for country
# and agricultural levels
totc_out <- rbind(t(sapply(totc_cntry, function(x) x[, 1])),
                  t(sapply(totc_crop, function(x) x[, 1])))
pnms <- c("Forest", "Secondary", "Shrubland", "Grassland", "Sparse")
knms <- rep(mcap, 2)
totc_out <- cbind.data.frame(knms, round(unname(totc_out), 2))
colnames(totc_out) <- c("Map", pnms)
totc_out <- cbind(Region = c(rep("Country", 4), rep("Agricultural", 4)), 
                  totc_out)
capt <- paste("Percent differences in total carbon stock estimates", 
              "calculated from the reference maps and from each of the four",
              "cropland maps. Differences are evaluated for total carbon",
              "estimates either at the country scale or over just the",
              "agricultural regions (cropland $>$0.05\\%), using",
              "the carbon densities of 5 different cover types to provide", 
              "the values for the non-agricultural portions of each pixel",  
              "(cover types indicated by column names).")
totc_xtab <- xtable(totc_out, caption = capt, digits = 1)
print(totc_xtab, type = "latex", caption.placement = "top",
      file = "paper/figures/totC-bias.tex", include.rownames = FALSE)

@@

# check error stats - do they match alternate approaches?
for(i in c("f1", "f25", "f10")) { # i <- "f1"
  for(j in c("sa30", "modmu", "geow")) { # j <- "modmu"
    for(k in c("forest", "shrub", "sparse", "second")) {  # k <- "second"
      print(paste("cross-checking calculations in", i, j, k))
      ref <- gti_agg[[i]][[1]]
      awgts <- area_wgts[[i]][[1]]
      rerror <- c_pct_diff[[i]][[j]]
      a1 <- bias_statsw(ref, awgts, rerror, LC, wm, "mu", 
                        aweight = FALSE)[, get(k)]
      a2 <- bias_statsw(ref, awgts, rerror, LC, wm, "mu", 
                        rweight = FALSE, aweight = FALSE)[, get(k)]
      a3 <- bias_statsw(ref, awgts, rerror, LC, wm, "mu")[, get(k)]
      c1 <- getValues(c_pct_diff[[i]][[j]][[k]])
      w1 <- getValues(gti_agg[[i]][[1]])
      w2 <- getValues(area_wgts[[i]][[1]])
      print("...non-area weighted mean matches?")
      print(a1 == round(weighted.mean(c1, w1, na.rm = TRUE), 2))
      print("...totally unweighted mean matches?")
      print(a2 == round(cellStats(rerror[[k]], mean), 2))
      print("...double weighted mean matches?")
      print(a3 == round(weighted.mean(c1, w1 * w2, na.rm = TRUE), 2))
    }
  }
}
save(cb_statsw_mua, cb_statsw_mu, file = fp(p_data, "carbon-werr.rda"))
````

@@

caption <- paste("Biases and mean absolute errors (as \\%) for",              
                 "evapotranspiration variables derived from a 29-year time",
                 "series calculated by the VIC model, including the average", 
                 "total ET for the", 
                 "3 months of the year when ET is highest, the annual mean", 
                 "and the minimum and maximum annual ETs in the time series.")
mutab_xtab <- xtable::xtable(mutab, digits = 1, caption = caption)
print(mutab_xtab, type = "latex", file = "paper/figures/et-bias.tex",
      tabular.environment = "longtable", floating = FALSE, 
      caption.placement = "top", include.rownames = FALSE)

et_err <- mutab
save(et_err, file = fp(p_data, "et-err-bias.rda"))
```

@@

# data.table calculations
gti_dt <- na.omit(as.data.table.raster(gtis, xy = TRUE))
setkey(gti_dt, prov)
cf <- gti_dt[, list("carea" = sum(f), "parea" = length(f), 
                    "cf" = sum(f) / length(f)), by = prov]
# cftest - cf[, 2:4, with = FALSE]  # close, but diff caused by few NAs in provr 
# data.table approach is much more efficient
```

@@

save(list = ls(), file = full_path(p_data, "yield-bias.rda"))
save(out_tab, file = fp(p_data, "yield-prod-accbias.rda"))
save(cyld_agg, cpagg1, file = full_path(p_data, "yieldprod-1km.rda"))

@@

# Impact of cropland errors on location

Evaluated in terms of how landcover map error impacts the ability to locate areas having a particular quantity of interest.

Derived carbon (section 6) and yield estimates (section 8).

```{r, eval=FALSE}
library(SAcropland)
library(xtable)
library(RColorBrewer)
library(spatstat)
p_root <- full_path(proj_root("SAcropland"), "SAcropland")
p_fig <- full_path(p_root, "paper/figures/")
p_data <- full_path(p_root, "external/ext_data/")
p_data2 <- full_path(p_root, "data/")
#p_carb <- full_path(p_root, "SAcropland/external/ext_data/carbon/")
# load(full_path(p_data, "yield-bias.rda"))

# yield and carbon data
load("external/ext_data/yieldprod-1km.rda")
load("external/ext_data/carbon-tier1.rda")
load("external/ext_data/cropland-1km.rda")
```

## Differences in location

If you are interested in selecting areas of highest yield/production/carbon potential, how far off are you relative to "truth". Use top quintile/decline to assess this, and then calculate mean nearest neighbor distance between two pixels of each map.

### Identify high value areas
```{r, eval = FALSE}
# top decile of...
# ...cropland
crclass <- lapply(cropl, function(x) {  # x <- cropl$sa30
  r <- x * (x > 0)
  r[r == 0] <- NA
  rq <- quantile(r, c(0, 0.9, 1))
  types <- cut(r, breaks = rq)
  types > 1
})

# ...yield
yclass <- lapply(cyld_agg$f1, function(x) {  # x <- cyld_agg$f1[[1]]
  r <- x * (x > 0)
  r[r == 0] <- NA
  rq <- quantile(r, c(0, 0.9, 1))
  types <- cut(r, breaks = rq)
  types > 1
})

# ...production
pclass <- lapply(cpagg1$f1, function(x) {  # x <- cyld_agg$f1[[1]]
  r <- x * (x > 0)
  r[r == 0] <- NA
  rq <- quantile(r, c(0, 0.9, 1))
  types <- cut(r, breaks = rq)
  types > 1
})

# ...carbon
cdat <- c(gti_c$f1, lc_c$f1)
cdatf <- lapply(cdat, function(x) {  # mask out non-cropland areas and take mu C
  msk <- x$forest < 99.6
  cmu <- calc(x, mean)
  raster::mask(cmu, msk, maskvalue = 0)
})
cclass <- lapply(cdatf, function(x) {  # x <- cyld_agg$f1[[1]]
  r <- x * (x > 0)
  r[r == 0] <- NA
  rq <- quantile(r, c(0, 0.9, 1))
  types <- cut(r, breaks = rq)
  types > 1
})
names(cclass) <- names(pclass)

# carbon efficiencies (C / yield)
effclass <- lapply(1:5, function(x) { # x <- 1
  cyld <- cyld_agg$f1[[x]]
  cyld[cyld == 0] <- NA
  cdatfc <- crop(cdatf[[x]], cyld)
  eff <- cdatfc / cyld  # carbon efficiency
  # eff[is.infinite(eff)] <- NA
  rq <- quantile(eff, c(0, 0.9, 1))
  types <- cut(eff, breaks = rq)
  types > 1
})
names(effclass) <- names(cclass)

### Calculate nearest-neighbor distances

Between GTI high value areas and each of the four LC-derived datasets. 
```{r, eval = FALSE}

# calculate distance between GTI and each other dataset's classes. 
# pms2a <- expand.grid(rep(list(0:1), 5))[-1, ] 
# pms2b <- pms2a[which(rowSums(pms2a) == 2 & pms2a$Var1 == 1), ]
# pms2b$cl <- c("YC1", "YC2", "YC3", "YC4")
# rownames(pms2b) <- 1:4

# Define neighborhood window
sa_owin <- owin(xrange = bbox(sa.shp)[1, ], yrange = bbox(sa.shp)[2, ],
                unitname = "meter")
# which1 <- function(x) x == 1  # selector function for r to xy

mudists <- lapply(list(crclass, yclass, pclass, cclass, effclass), function(x) {
  # x <- cclass
  mudist <- sapply(2:5, function(y) {  # y <- 2
    print(paste0("...", y))
    a <- rasterToPoints(x$gti, fun = function(x) x == 1)
    b <- rasterToPoints(x[[y]], fun = function(x) x == 1)
    pps <- lapply(list(a, b), function(z) {
      ppp(x = z[, 1], y = z[, 2], window = sa_owin)
    })
    names(pps) <- c("gti", names(x)[y])
    reord <- sort(sapply(pps, function(i) i$n), decreasing = TRUE)
    ppnn <- nncross(pps[[names(reord)[1]]], pps[[names(reord)[2]]])
    mean(ppnn$dist) / 1000
  })
  names(mudist) <- names(x)[2:5]
  mudist
})  
names(mudists) <- c("cropland", "yield", "prod", "carb", "eff")

# average km off
mudvec <- unlist(mudists)
median(mudvec[!like(names(mudvec), "sa30")])
# mean(mudvec)

# plot(stack(yclass))
# plot(is.na(yclass[[1]]) - is.na(yclass[[2]]))
# plot(is.na(cyld_agg$f1$gti) - is.na(cyld_agg$f1$geow))

# output plot
cols <- c("red", "orange3", "green4", "blue")
pcol <- makeTransparent(cols, alpha = c(120))
pcol2 <- makeTransparent(cols, alpha = c(30))

plot(1:4, pch = 20, col = pcol)
bs <- do.call(rbind, mudists[c(1, 2, 4)])
lcnms <- c("SA LC", "GlobCover", "MODIS", "Geowiki")

pdf(full_path(p_fig, "location_offset.pdf"), height = 3.5, width = 4, 
    bg = "transparent")
par(mar = c(2, 3.5, 1, 0), bg = "transparent")
bp <- barplot(bs, beside = TRUE, col = ggplot2:::interleave(cols, pcol, pcol2), 
              las = 2, border = "transparent", xaxt = "n", ylab = "", 
              ylim = c(0, 18), yaxt = "n")
axis(1, at = colMeans(bp), labels = lcnms, lty = 0, cex.axis = 0.9, 
     mgp = c(2, 0.25, 0))
axis(2, at = seq(0, 18, 2), labels = seq(0, 18, 2), las = 2)
mtext("km", side = 2, line = 2.25)
legend(x = 12.5, y = 18, legend = rep("", 4), pch = 15, col = cols, adj = 0,
       pt.cex = 1.5, bty = "n", cex = 0.8, x.intersp = 0, horiz = TRUE)
legend(x = 12.5, y = 17.25, legend = rep("", 4), pch = 15, adj = 0, col = pcol, 
       pt.cex = 1.5, bty = "n", cex = 0.8, horiz = TRUE, x.intersp = 0)
legend(x = 12.5, y = 16.5, legend = rep("", 4), pch = 15, adj = 0, col = pcol2, 
       pt.cex = 1.5, bty = "n", cex = 0.8, horiz = TRUE, x.intersp = 0)
text(x = 13, y = 17, labels = "Cropland", pos = 2, cex= 0.8)
text(x = 13, y = 16.25, labels = "Yield", pos = 2, cex = 0.8)
text(x = 13, y = 15.5, labels = "Carbon", pos = 2, cex= 0.8)
dev.off()

@@

```{r, message=FALSE}
library(rgdal)
library(SAcropland)
library(rgeos)
library(lmisc)

@@

## Area of sub-Saharan Africa and South Africa's share of that area
```{r}
eco <- readOGR(dsn = fp(p_dat, "africa_ecofloristic_zones.sqlite"), 
               layer = "africa_ecofloristic_zones")
eco@proj4string <- CRS(projection(raster(nrow = 1, ncol = 1)))
af <- readOGR(dsn = fp(p_dat, "africa_countries_alb.sqlite"), 
               layer = "africa_countries_alb")
af@data <- af@data[, c(1, 3:4, 6:7)]
ecoalb <- spTransform(eco, af@proj4string)

@@

nosahara <- ecoalb[-sahara, ]
# plot(nosahara, col = "red")

ovs <- which(!is.na(over(nosahara, ssa)))
ssaeco <- nosahara[ovs, ]
ssaeco <- ssaeco[-1, ]  # drop a couple Saharan mountains
ssaeco <- ssaeco[-1, ]
# plot(ssaeco[ssaeco@data$gez_term == "Tropical mountain system", ][1, ])
# plot(ssa)
# plot(ssaeco, col = "red", add = TRUE)

@@

```{r, eval=FALSE, echo = FALSE}
a <- sample(1:100, size = 20)
b <- sample(1:80, size = 20)
mean(a - b)
sum(a) / sum(b)
```

## Calculation of error propagation
```{r}
load(fp(p_dat, "cropland-werr-2011.rda"))
load(fp(p_dat, "yield-prod-accbias.rda"))
load(fp(p_dat, "et-err-bias.rda"))
load(fp(p_dat, "carbon-werr.rda"))

cland <- bacc2011
yprod <- as.data.table(out_tab)[Region == "Density"]
carb <- rbind(cb_statsw_mu, cb_statsw_mua)

# Reshape error stats
# yield/production 
yp1 <- melt(yprod, id.vars = c("Map", "Metric", "Variable"), 
            measure.vars = names(yprod)[5:10])
yp2 <- dcast(yp1, formula = Metric + Variable + variable ~ Map)
setcolorder(yp2, neworder = c(1:3, ncol(yp2), 5:6, 4))
setnames(yp2, names(yp2), c("stnm", "var", "ol", names(cland)[-c(1:2)]))

snms <- names(cland)[-c(1:2)]
lev <- cland[stnm == "mu", ol]

# Production and yield propagation
yp_prop <- rbindlist(lapply(c("Yield", "Production"), function(x) {  
  o <- data.frame(t(sapply(snms, function(y) {  # y <- "sa30"
    emag <- yp2[var == x & stnm == "MAE", get(y)] / 
      cland[stnm == "mua", get(y)] 
    c(emag, mean(emag))
  })))
  o <- cbind(snms, round(o, 2))
  colnames(o) <- c("map", lev, "mu")
  data.table(cbind.data.frame("var" = x, o))
}))

# Carbon differences
c_prop <- rbindlist(lapply(snms, function(x) {  # x <- "sa30"
  dat <- carb[stnm == "MAE" & map == x, names(carb)[-c(1:3)], with = FALSE]
  o <- dat[, lapply(.SD, function(y) y / cland[stnm == "mua", get(x)]), 
           .SDcols = names(dat)]
  o <- round(rbind(o, data.table(t(colMeans(o)))), 2)
  o <- cbind("ol" = c(lev, "mu"), o)
  cbind("map" = x, o)
  # dat[, second] / cland[stnm == "mua", get(x)]
}))

# et propagation
et_prop <- round(et_err[Variable == "Annual Mean", MAE] / 
  cland[ol == "f25" & stnm == "mua", snms, with = FALSE], 2)

yp_prop
c_prop
et_prop
```
